---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggzcql

<!-- badges: start -->
<!-- badges: end -->

`ggzcql` provides color palettes and themes for `ggplot2`, following the design patterns of [`ggsci`](https://github.com/nanxstats/ggsci).

## Palette Colors

The `zcql` palette features:
- **Background Theme Color**: `#F3B665` (Sunlit Clay)
- **Palette Colors**:
  1. `#2AA4E5` (Fresh Sky)
  2. `#80C79A` (Celadon)
  3. `#856A3B` (Olive Wood)
  4. `#D7FEBF` (Tea Green)

## Installation

You can install the development version of `ggzcql` from GitHub:

```r
# install.packages("pak")
pak::pak("nanxstats/ggzcql")
```

## Example

This example demonstrates how to use `scale_color_zcql()` and `theme_zcql()` in a `ggplot2` plot:

```{r example-plot, fig.height = 5, fig.width = 7}
library(ggplot2)
library(ggzcql)

ggplot(iris, aes(Sepal.Length, Sepal.Width, color = Species)) +
  geom_point(size = 3) +
  scale_color_zcql() +
  theme_zcql()
```
